### 2018-02-20 Sections/cryptowars.tex
RSA all added
crypto

Importantly, the secrecy of the one-time-pad\index{One-time pad cipher} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2.
\end{align}
Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

\comment{Explain RSA algorithm}

\comment{Size of ciphertext is bigger than plaintext}

@@

RSA \cite{bib:RSA} was the first published public-key cryptographic protocol, and forms the backbone for most encryption used on the internet today. It achieves its security based on the belief that factorising large integers into constituent primes is a computationally hard problem -- a so-called `trapdoor function'\index{Trapdoor function}. The private key comprises two prime numbers, which are multiplied together to obtain the public key. It is clear that to obtain the private key from the public key would require solving the integer factorisation problem, which is presumed to be intractable.

Since RSA, numerous other public-key cryptosystems have been developed, based on different choices of trapdoor function. However, RSA remains the most widely used public-key cipher.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item 
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item 
\item $\Box$
\end{enumerate}
}}}
\caption{} \label{alg:RSA}
\end{table}

@@

In the near future, as QKD schemes begin their rollout in space and on Earth, random bits from the QKD implementation will be very expensive and exhibit low bandwidth. Suppose we wanted to securely videoconference across the globe. For just a single user this would require megabits per second of shared random bits, which will quickly saturate the capacity of overhead quantum satellites. Instead, let us use the QKD system to securely share just a 256-bit private \textit{session key}\index{Session key} between two users. This is subsequently employed for AES-256 encryption that operates entirely over the classical network, which we regard as extremely cheap. Importantly, unlike one-time-pad implementations, this session key may be reused. Now we have a hybrid system which is not quantum-compromised, but which overcomes the cost and bandwidth issues associated with upcoming QKD networks.

@@

On the other hand, if a $\hat{Z}$ gate were applied to any one qubit, this would flip the parity outcome. Note that a GHZ transforms according to,
\begin{align}
	\hat{Z}_i \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}) \to \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} - \ket{1}^{\otimes n}),
\end{align}
for any qubit $i$. This invariance in the location of the $\hat{Z}$ gate is the basis for the anonymity of the protocol. If a user wishes to broadcast `0' he does nothing, whereas if we wishes to broadcast `1' he applies the $\hat{Z}$ gate to his local qubit.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \ket{\mathrm{GHZ}}$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = \big($\sum_i$ outcome$_i$\big)\,mod\,2
\item return(parity)
\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

@@

>>>>

Importantly, the secrecy of the one-time-pad\index{One-time pad cipher} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

@@

RSA \cite{bib:RSA} was the first published public-key cryptographic protocol, and forms the backbone for most encryption used on the internet today. It achieves its security based on the belief that factorising large integers into constituent primes is a computationally hard problem -- a so-called `trapdoor function'\index{Trapdoor function}. The algorithm is built upon number theory using modular arithmetic, shown in Alg.~\ref{alg:RSA}.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function RSAGenerateKey():
\begin{enumerate}
\item $p$ = randomPrime()
\item $q$ = randomPrime()
\item Ensure $p\neq q$
\item $n = pq$
\item $\lambda = \mathrm{lcm}(p-1,q-1)$
\item $e = \mathrm{coprime}(\lambda) \,\,\mathrm{s.t} \,\,e<\lambda$
\item $d = e^{-1}\,(\mathrm{mod} \, \lambda)$
\item publicKey = $\{n,e\}$
\item privatKey = $\{n,d\}$
\item return(publicKey,privateKey)
\item $\Box$	
\end{enumerate}
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item $\mathtt{cipertext} = \mathtt{plaintext}^e \, (\mathrm{mod} \, n$)
\item return(ciphertext)
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item $\mathtt{plaintext} = \mathtt{ciphertext}^d \, (\mathrm{mod} \, n)$
\item return(plaintext)
\item $\Box$
\end{enumerate}
}}}
\caption{Number-theoretic algorithms based on modular arithmetic for RSA key generation, encryption and decryption.} \label{alg:RSA}
\end{table}

A downside of RSA is that ciphertexts are in general much longer than plaintexts, unlike private-key protocols where the ciphertext is always the same length as the plaintextx. For this reason it is typically not used to directly encrypt long messages, since the memory overhead would be undesirable. Instead, RSA is typically employed in conjunction with private-key cryptography in a key exchange protocol\index{Key exchange protocol}. Here the public-key system communicates a private \textit{session key}\index{Session key} between parties, which is subsequently employ in a private-key protocol, without incurring the memory overhead that RSA does.

Since RSA, numerous other public-key cryptosystems have been developed, based on different choices of trapdoor function. Most notably, elliptic curve cryptography\index{Elliptic curve cryptography} has gained much attention. However, RSA remains the most widely used and well studied public-key cipher.

@@

In the near future, as QKD schemes begin their rollout in space and on Earth, random bits from the QKD implementation will be very expensive and exhibit low bandwidth. Suppose we wanted to securely videoconference across the globe. For just a single user this would require megabits per second of shared random bits, which will quickly saturate the capacity of overhead quantum satellites. Instead, let us use the QKD system to securely share just a 256-bit private session key\index{Session key} between two users. This is subsequently employed for AES-256 encryption that operates entirely over the classical network, which we regard as extremely cheap. Importantly, unlike one-time-pad implementations, this session key may be reused. Now we have a hybrid system which is not quantum-compromised, but which overcomes the cost and bandwidth issues associated with upcoming QKD networks.

@@

On the other hand, if a $\hat{Z}$ gate were applied to any one qubit, this would flip the parity outcome. Note that a GHZ transforms according to,
\begin{align}
	\hat{Z}_i \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}) \to \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} - \ket{1}^{\otimes n})\,\,\forall \, i,
\end{align}
for any qubit $i$. This invariance in the location of the $\hat{Z}$ gate is the basis for the anonymity of the protocol. If a user wishes to broadcast `0' he does nothing, whereas if he wishes to broadcast `1' he applies the $\hat{Z}$ gate to his local qubit.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \ket{\mathrm{GHZ}}$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

@@

%
% Attacks On Quantum Cryptography
%

\subsection{Attacks on quantum cryptography}

\comment{To do}
